% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      %this creates the heading for the acknowlegments
%This thesis was performed in close collaboration with ANDRITZ HYDRO GmbH based on their experience and tools.
I would like to express my deep and sincere gratitude to my supervisor, Professor Kyriakos Giannakoglou Ph.D., Head of Parallel CFD \& Optimization Unit, School of Mechanical Engineering, National Technical University of Athens. His wide knowledge and structured way of thinking have been of great value for me. His understanding, encouraging and personal guidance have provided a good basis for the present thesis.

I am deeply grateful to Erwin Oberbichler, Simon Weissenberger and Peter Grafenberger for guiding me into the inner workings of hydraulic turbines and above all sharing their wisdom and knowledge on what the optimum turbine should really be. I also wish to thank all of my colleges in Andritz Linz for their detailed and constructive comments, and for their important support throughout this work. 

I wish to express my warm and sincere thanks to Arno Gehrer for sharing his ideas and concepts on optimization regarding hydraulic pumps and pump-turbines and Irida Skouteropoulou and Kostas Tsiakas for implementing and testing them. Furthermore I would like to thank  Florent Champet for his ideas concerning optimization of pelton distributors and the number of evaluation tools used within the multilevel optimization scheme. 

My warm thanks are due to Paul Pieringer, Simon Weissenberger and Livia Koch for providing the efficient and robust parameterization, grid generation and flow solver tools used for the industrial scale hydraulic optimization procedures.      

I warmly thank Ioannis Kampolis for laying the stable foundations on witch this thesis has build upon, and guiding me on my first years as a PhD student. I would also like to thank Varvara Asouti for her valuable help in the field of Evolutionary Algorithms.

During this work I have collaborated with many colleagues for whom I have great regard, and I wish to extend my warmest thanks to all those who have helped me with my work in Parallel CFD \& Optimization Unit, School of Mechanical Engineering, National Technical University of Athens. Without exception, all new ideas/methods presented in this thesis have their roots in constructive conversations with you and for that I warmly thank you.   

Last but not least, I owe my loving thanks to my family, Antonis, Anna and Nektaria Kyriacou. They have lost a lot due to my research abroad. Without their encouragement and understanding it would have been impossible for me to finish this work. 

The financial support of ANDRITZ HYDRO and the EU project named "HYDROACTION-Development and laboratory testing of improved action and Matrix hydro turbines designed by advanced analysis and optimization tools" (PROJECT NUMBER : 211983) is gratefully acknowledged.

\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------


